### 2019-06-28 Memoria/Chapters/ExperimentalSetup.tex
Correcciones y nuevas secciones

In this section we present the experimental setup used to compare the two new proposals introduced in Part \ref{pt:NewProposals} with the current state of the art. We will start by briefly introducing the state-of-the-art methods. Afterwards we specify the dataset used in experimentation, as well as the constraint sets and the results evaluation method. We also include the required specifications to replicate the experiments.

\subsection{State-of-the-art Methods} \label{sec:SOTA}

@@

\section{Datasets}

@@

Classification datasets are commonly used in the literature to test constrained clustering algorithms; the reason behind this is that they enable us to generate constraints with respect to the true labels (see Section \ref{sec:ConstGent}). They also facilitate an easy evaluation of the quality of the algorithm by means of measures like the Adjusted Rand Index (see Section \ref{sec:EvalMet}).

\section{Constraint Generation} \label{sec:ConstGent}

@@

We will generate, for each dataset, three different sets of constraints---$CS_{10}$, $CS_{15}$ and $CS_{20}$---that will be associated with three small percentages of the size of the dataset: 10\%, 15\% and 20\%. With $n_f$ being the fraction of the size of the dataset associated with each of these percentages, the formula $\frac{n_f(n_f-1)}{2}$ tells us how many artificial constraints will be created for each constraint set; this number is equivalent to how many edges a complete graph with $n_f$ vertices would have.

The random allocation of constraints has a potential advantage over simply using the constraints contained in an $n_f$-vertex complete graph: there is a lower probability of biasing the constraint set towards having classes with poor representation in it. Table \ref{tab:constraints} shows the number of constraints of each type obtained for each dataset.

@@

Note that the greater the number of classes present in the dataset, the fewer ML constraints obtained with the method proposed in \cite{wagstaff2001constrained}. This is because the probability of randomly choosing two individuals from the same class decreases as the number of classes present in the dataset increases.

\subsection{Evaluation Method} \label{sec:EvalMet}

Since we have the true labels associated to each of the datasets, we can use them to evaluate the results provided by each method. We will use the \acf{ARI} to measure the accuracy of the predictions resulting from each method we test \cite{hubert1985comparing}. The basic Rand Index computes the degree of agreement between two partitions $C_1$ and $C_2$ of a given dataset $X$. $C_1$ and $C_2$ are viewed as collections of $n(n - 1)/2$ pairwise decisions \cite{rand1971objective}.

@@

In order to validate the results which will be presented in Section \ref{sec:results} we will use Bayesian statistical tests, instead of the classic Null Hypothesis Statistical Tests (NHST). In \cite{benavoli2017time} we find an in-depth analysis of the disadvantages of NHST, and a new model is proposed for carrying out comparisons researchers are interested in. \textit{"In a nutshell: NHST do not answer the question we ask"}. To put it clear, the disadvantages of the NHST that the authors highlight in \cite{benavoli2017time} are based on the trap of black-and-white thinking, this is: to reject, or not to reject?

To start with, NHST do not provide us with the probabilities associated to the analyzed hypotheses, and therefore it is not possible to answer the question: what is the probability that two methods are different? Another pitfall of NHST is that, with a sufficiently large number of observations, it is possible to reject almost any hypothesis. This is because the p-value does not allow us to separate between the effective size and the sample size, which is established by the researcher.

Also, NHST do not provide information about the magnitude of the effects and the uncertainty of its estimate. As a consequence, NHST may reject hypotheses despite very small effects, or even if there is significant uncertainty in the magnitude of the effects.

Furthermore, and this is a situation that all researchers have faced, NHST do not provide any information about the null hypothesis! That is: What can we conclude when NHST do not reject the null hypothesis? We can not infer anything since NHST can not provide evidence in its favor.

Finally, there are two other problems that researchers face when performing NHST. The first one is the choice of the significance level $\alpha$, for which there are no objective guidelines despite being critical to the test results. The second one is the need to previously formalize the intentions of the sampling of the results, which are usually fixed a posteriori; this could lead to a misreading of said results.

As shown in \cite{benavoli2017time}, most of these problems can be avoided by using Bayesian tests instead of NHST. In particular we will use the Bayesian sign test, which is the Bayesian version of the frequentist non-parametric sign test. To make use of it we will employ the R package \texttt{rNPBST}, whose documentation and guide can be found in \cite{carrasco2017rnpbst}.

@@

\section{Calibration}

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{>{\centering\arraybackslash}c m{5cm} cc}
			\hline
			Parameter & Meaning & \acs{BRKGA}$_{CC}$ & \acs{SHADE}$_{CC}$ \\
			\hline
			$|P|$ & Population size & 100 & 100 \\
			Evals & Fitness function evaluations & 300000 & 300000 \\
			$P_e$ & Size of the elite set in population & $0.2 * |P|$ & $0.25 * |P|$ \\
			$P_m$ & Number of mutants to be introduced in the population in each generation & $0.2 * |P|$ & - \\
			$p_\text{inherit}$ & Probability that a feature is inherited from an elite parent & $50\%$ & - \\
			$k$ & Output partition number of clusters & \multicolumn{2}{m{4cm}}{No. Classes (Table \ref{tab:datasets})} \\
			\hline

@@

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{>{\centering\arraybackslash}c m{6cm} c}
			\hline
			Parameter & Meaning & Value \\
			\hline
			Evals & Fitness function evaluations & 300000 \\
			$p_s$ & Segment size for the mutation operator & $0.3 \times n$ \\
			$p_m$ & Maximum number of neighbors generated in each call to the LS procedure & Evals $\times 0.01$ \\
			$p_r$ & Probability that a feature is selected from $m_b$ for recombination & $0.3$ \\
			$\xi$ & Reinitialization method tolerance & $0.2$ \\
			$k$ & Output partition number of clusters & No. Classes (Table \ref{tab:datasets}) \\
			\hline

@@

>>>>

In this chapter we present the experimental setup used to compare the two new proposals introduced in Chapter \ref{ch:NewProposals} with the current state of the art. We will start by briefly introducing the state-of-the-art methods in Section \ref{sec:SOTA}. Afterwards we specify the dataset used in experimentation (Section \ref{sec:Datasets}), as well as the constraint sets (Section \ref{sec:ConstGen}) and the results evaluation method (Section \ref{sec:EvalMet}). In Section \ref{sec:ValidtnMethod} we introduce the validation method we will apply to the results. We also include the required specifications to replicate the experiments in Section \ref{sec:Calibration}.

\section{State-of-the-art Methods} \label{sec:SOTA}

@@

\section{Datasets} \label{sec:Datasets}

@@

Classification datasets are commonly used in the literature to test constrained clustering algorithms; the reason behind this is that they enable us to generate constraints with respect to the true labels (see Section \ref{sec:ConstGen}). They also facilitate an easy evaluation of the quality of the algorithm by means of measures like the Adjusted Rand Index (see Section \ref{sec:EvalMet}).

\section{Constraint Generation} \label{sec:ConstGen}

@@

We will generate, for each dataset, three different sets of constraints---$CS_{10}$, $CS_{15}$ and $CS_{20}$---that will be associated with three small percentages of the size of the dataset: 10\%, 15\% and 20\%. With $n_f$ being the fraction of the size of the dataset associated with each of these percentages, the formula $(n_f(n_f-1))/2$ tells us how many artificial constraints will be created for each constraint set; this number is equivalent to how many edges a complete graph with $n_f$ vertices would have. Table \ref{tab:constraints} shows the number of constraints of each type obtained for each dataset.

@@

The random allocation of constraints has a potential advantage over simply using the constraints contained in an $n_f$-vertex complete graph: there is a lower probability of biasing the constraint set towards having classes with poor representation in it. Note that the greater the number of classes present in the dataset, the fewer ML constraints obtained with the method proposed in \cite{wagstaff2001constrained}. This is because the probability of randomly choosing two individuals from the same class decreases as the number of classes present in the dataset increases. Figure \ref{fig:IrisConst} displays a visual representation of the constraint sets generated for the Iris dataset.

\begin{figure}[bth]
	\myfloatalign
	\subfloat[$CS_{10}$ \acs{ML} constraints]
	{\includegraphics[width=0.45\linewidth]{gfx/ExpSetup/ML10.png}} 
	\subfloat[$CS_{10}$ \acs{CL} constraints]
	{\includegraphics[width=0.45\linewidth]{gfx/ExpSetup/CL10.png}} \quad
	\subfloat[$CS_{15}$ \acs{ML} constraints]
	{\includegraphics[width=0.45\linewidth]{gfx/ExpSetup/ML15.png}} 
	\subfloat[$CS_{15}$ \acs{CL} constraints]
	{\includegraphics[width=0.45\linewidth]{gfx/ExpSetup/CL15.png}} \quad
	\subfloat[$CS_{20}$ \acs{ML} constraints]
	{\includegraphics[width=0.45\linewidth]{gfx/ExpSetup/ML20.png}} 
	\subfloat[$CS_{20}$ \acs{CL} constraints]
	{\includegraphics[width=0.45\linewidth]{gfx/ExpSetup/CL20.png}} 
	\caption{Visual representation of the three constraints sets the Iris dataset.}
	\label{fig:IrisConst}
\end{figure}

\section{Evaluation Method} \label{sec:EvalMet}

Since we have the true labels associated with each of the datasets, we can use them to evaluate the results provided by each method. We will use the \acf{ARI} to measure the accuracy of the predictions resulting from each method we test \cite{hubert1985comparing}. The basic Rand Index computes the degree of agreement between two partitions $C_1$ and $C_2$ of a given dataset $X$. $C_1$ and $C_2$ are viewed as collections of $n(n - 1)/2$ pairwise decisions \cite{rand1971objective}.

@@

In order to validate the results which will be presented in Section \ref{sec:results} we will use Bayesian statistical tests, instead of the classic \acf{NHST}. In \cite{benavoli2017time} we find an in-depth analysis of the disadvantages of \acs{NHST}, and a new model is proposed for carrying out comparisons researchers are interested in. \textit{"In a nutshell: \acs{NHST} do not answer the question we ask"}. To put it clear, the disadvantages of the \acs{NHST} that the authors highlight in \cite{benavoli2017time} are based on the trap of black-and-white thinking, this is: to reject, or not to reject?

To start with, \acs{NHST} do not provide us with the probabilities associated to the analyzed hypotheses, and therefore it is not possible to answer the question: what is the probability that two methods are different? Another pitfall of \acs{NHST} is that, with a sufficiently large number of observations, it is possible to reject almost any hypothesis. This is because the p-value does not allow us to separate between the effective size and the sample size, which is established by the researcher.

Also, \acs{NHST} do not provide information about the magnitude of the effects and the uncertainty of its estimate. As a consequence, \acs{NHST} may reject hypotheses despite very small effects, or even if there is significant uncertainty in the magnitude of the effects.

Furthermore, and this is a situation that all researchers have faced, \acs{NHST} do not provide any information about the null hypothesis! That is: What can we conclude when \acs{NHST} do not reject the null hypothesis? We can not infer anything since \acs{NHST} can not provide evidence in its favor.

Finally, there are two other problems that researchers face when performing \acs{NHST}. The first one is the choice of the significance level $\alpha$, for which there are no objective guidelines despite being critical to the test results. The second one is the need to previously formalize the intentions of the sampling of the results, which are usually fixed a posteriori; this could lead to a misreading of said results.

As shown in \cite{benavoli2017time}, most of these problems can be avoided by using Bayesian tests instead of \acs{NHST}. In particular we will use the Bayesian sign test, which is the Bayesian version of the frequentist non-parametric sign test. To make use of it we will employ the R package \texttt{rNPBST}, whose documentation and guide can be found in \cite{carrasco2017rnpbst}.

@@

\section{Calibration} \label{sec:Calibration}

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	%\resizebox{\textwidth}{!}{
		\begin{tabular}{>{\centering\arraybackslash}c >{\arraybackslash}L{5cm} cc}
			\hline
			Parameter & Meaning & \acs{BRKGA}$_{CC}$ & \acs{SHADE}$_{CC}$ \\
			\hline
			$|P|$ & Population size & 100 & 100 \\
			Evals & Fitness function evaluations & 300000 & 300000 \\
			$P_e$ & Size of the elite set in population & $0.2 * |P|$ & $0.25 * |P|$ \\
			$P_m$ & Number of mutants to be introduced in the population in each generation & $0.2 * |P|$ & - \\
			$p_\text{inherit}$ & Probability that a feature is inherited from an elite parent & $50\%$ & - \\
			$k$ & Output partition number of clusters & \multicolumn{2}{m{4cm}}{No. Classes (Table \ref{tab:datasets})} \\
			\hline

	\end{tabular}%}
	%\end{adjustwidth}

@@

\newpage

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{c L{6cm} c}
			\hline
			Parameter & Meaning & Value \\
			\hline
			Evals & Fitness function evaluations & 300000 \\
			$p_s$ & Segment size for the mutation operator & $0.3 \times n$ \\
			$p_m$ & Maximum number of neighbors generated in each call to the LS procedure & Evals $\times 0.01$ \\
			$p_r$ & Probability that a feature is selected from $m_b$ for recombination & $0.3$ \\
			$\xi$ & Reinitialization method tolerance & $0.2$ \\
			$k$ & Output partition number of clusters & No. Classes (Table \ref{tab:datasets}) \\
			\hline

@@

\clearpage
